Further Evidence of Modified Spin-down in Sun-like Stars:\\Pile-ups in the Temperature--Period Distribution

### 2022-01-20 src/ms.tex
revising ages figure

We additionally selected stars on the long-period pile-up from the \lamostmcq sample by selecting stars with periods within 5\% of the Ro~=~1.3 curve (which traces the center of the highest density contour in Figure~\ref{fig:kde}) , 5500~K~$<$~\teff~$<$~6500~K, and 4~dex~$<$~\logg~$<$~4.75~dex. While ages for the \lamostkep sample are not available, the broad distribution of these stars in the spectroscopic H-R diagram supports the inference from the CKS sample that the long-period pile-up is populated by stars with a broad range of ages (Figure~\ref{fig:ages}). Interestingly, the solar \teff and \logg values appear to be wholly consistent with the distribution of long-period pile-up stars. We discuss the Sun in context of the long-period pile-up further in \S\ref{subsec:thesun}.

>>>>

We additionally selected stars on the long-period pile-up from the \lamostmcq sample by selecting stars with periods within 5\% of the Ro~=~1.3 curve (which traces the center of the highest density contour in Figure~\ref{fig:kde}) , 5500~K~$<$~\teff~$<$~6500~K, and 4.1~dex~$<$~\logg~$<$~4.75~dex. While ages for the \lamostkep sample are not available, the broad distribution of these stars in the spectroscopic H-R diagram supports the inference from the CKS sample that the long-period pile-up is populated by stars with a broad range of ages (Figure~\ref{fig:ages}). Interestingly, the solar \teff and \logg values appear to be wholly consistent with the distribution of long-period pile-up stars. We discuss the Sun in context of the long-period pile-up further in \S\ref{subsec:thesun}.
